A Study on Common Bug Fix Patterns in Rust

### 2022-10-13 sections/related.tex
5.1

Automated program repair aims to debug faulty source code without human involvement, sometimes using test cases to guide the repair. Before a repair tool can modify some code, it will typically use a fault localization module to find bug locations. A fault localization module ranks program statements based on their suspiciousness; one example is Tarantula by Jones and Harrold~\cite{jones2005empirical}. Suspiciousness is calculated using a statistical model which relies on the observation that buggy statements are executed mostly by failed test cases~\cite{naish2009spectral,xie2013theoretical}.

Researchers have proposed different methods for code repair, each of which follows a different mindset. Following the taxonomy propsed by~\cite{liu2018survey}, we briefly present a number of mindsets, and will discuss how having a set of predefined fix patterns can be beneficial for repair purposes.

\subsection{Search-Based Program Repair}
One line of research in program repair follows the competent programmer hypothesis~\cite{gopinath2014mutant}: syntactically, a faulty programs is not that far away from its correct version. This hypothesis suggests the search-based program repair mindset. If the hypothesis holds, we can develop mutation operators (which change an expression or a statement) and apply them to a list of fault locations provided by the fault localization module. If mutation of a statement does not result in complete success after running the test cases, we assume that the statement is correct and move on to the next fault location. Knowing bug producing patterns help the researchers to design more creative mutation operators that leverage domain specific insights.

Use of mutation operators in program repair became popular when Weimer et al.~\cite{forrest2009genetic,nguyen2009using} developed GenProg, a program repair tool that uses genetic programming. The main idea behind this tool is that statements follow certain patterns in a codebase. Therefore, if we find the correct version of a faulty statement somewhere in the program, we can use it to fix our program. This tool showed promising results as it managed to find patches without any additional annotations or human involvements.

However, Arcuri and Briand~\cite{arcuri2011practical} suspected the effectiveness of genetic programming in GenProg, as the tool mostly found the patch in its random initialization phase, in other words, before the evolution begins. Through developing TrpAutoRepair~\cite{qi2013efficient} and RSRepair~\cite{qi2014strength}, the test case prioritization is necessary while using genetic programming, as fitness evaluation is an expensive part of the repair pipeline.

Tan and Rovehoudhury~\cite{tan2015relifix} used mutation repairing for fixing regression bugs. They categorized common code changes in real-world regressions after studying 73 program evolution benchmarks. They used this categorization to design mutation operators, and chose them based on the faulty location’s to repair the program.

>>>>

Automated program repair aims to debug faulty source code without human involvement, sometimes using test cases to guide the repair. Before a repair tool modifies code, it will typically use a fault localization module to find fault locations. A fault localization module ranks program statements based on suspiciousness; one example is Tarantula by Jones and Harrold~\cite{jones2005empirical}. Suspiciousness is calculated using a statistical model which relies on the observation that buggy statements are executed mostly by failed test cases~\cite{naish2009spectral,xie2013theoretical}.

Researchers have proposed different methods for code repair, each of which can be said to follow a different mindset. Following the taxonomy propsed by~\cite{liu2018survey}, we briefly present a number of mindsets, and will discuss how having a set of predefined fix patterns can be beneficial for repair purposes.

\subsection{Search-Based Program Repair}
One line of research in program repair follows the competent programmer hypothesis~\cite{gopinath2014mutant}: syntactically, a faulty program is not that far away from its correct version. This hypothesis suggests the search-based program repair mindset. If the hypothesis holds, we can develop mutation operators (which change an expression or a statement) and apply them to a list of fault locations provided by the fault localization module. So, we loop through possible mutations; if the mutation of a statement does not cause all expected-successful test cases to succeed, we assume that the statement is correct and move on to the next fault location. Having a set of bug-producing patterns, like the ones we are proposing, will help researchers design targetted mutation operators that leverage domain specific insights.

Use of mutation operators in program repair became popular when Weimer et al.~\cite{forrest2009genetic,nguyen2009using} developed GenProg, a program repair tool that uses genetic programming. The main idea behind this tool is that statements follow certain patterns in a codebase. Therefore, if we find the correct version of a faulty statement somewhere in the program, we can use that version in place of the faulty original. This tool showed promising results as it managed to find patches without any additional annotations or human involvements.

However, Arcuri and Briand~\cite{arcuri2011practical} observed that GenProg mostly found the patch while carrying out random initialization---that is, before GenProg's evolution begins. Their tools TrpAutoRepair~\cite{qi2013efficient} and RSRepair~\cite{qi2014strength} advocate that test case prioritization is necessary while using genetic programming, as fitness evaluation is an expensive part of the repair pipeline.

Tan and Rovehoudhury~\cite{tan2015relifix} used mutation repairing for fixing regression bugs. They categorized common code changes in real-world regressions after studying 73 program evolution benchmarks; our approach also yields a set of common code changes, for Rust, using a different set of changes. Tan and Rovehoudhury used their categorization to design mutation operators, and chose them based on the faulty locations to repair the program.
